%----------------------------------------------------------------------------------------
%	SECTION TITLE
%----------------------------------------------------------------------------------------

\cvsection{Experience}

%----------------------------------------------------------------------------------------
%	SECTION CONTENT
%----------------------------------------------------------------------------------------

\begin{cventries}

%------------------------------------------------    

\cventry
{Senior Software Developer} % Job title
{Seagate} % Organization
{Jalisco, Mexico} % Location
{Sep. 2015 - Present } % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Maintained software solution to test high performance platforms in c, perl and python.}
\item {Developed tools to process data files and work flow with python.}
\end{cvitems}
}

%------------------------------------------------

\cventry
{Software Engineer \& Security Researcher} % Job title
{Intel} % Organization
{Jalisco, Mexico} % Location
{Sep. 2014 -  Jul. 2015} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Implemented software to verify the security state of Intel architecture in C and python.}
\item {Improved functionality of a tool to check the security state of client platform to work with servers in C and perl.}
\item {Improved the tool functionality for UEFI/LINUX to work with features only available for windows OS using c, python and perl.}
\item {Launch first version of a tool to manage the security in IP designs in python.}
\end{cvitems}
}

%------------------------------------------------

\cventry
{Software Engineer Developer - Team lead } % Job title
{Centro de Soluciones Inalambricas} % Organization
{Yucatan, Mexico} % Location
{Aug. 2010 - Sep. 2012} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Implemented a new approach for geolocalization by web page, using jquery, css5 and DHTML.}
\item {Developed web services to work with asynchronous calls by js/jquery and movile devices with .NET framework / IIS server.}
\item {Improved the scope of the web tool, with a project to homologateall the solutions}
\item {Developed of querys for Data Bases with SQL DBM}
\end{cvitems} 
}

%------------------------------------------------

\cventry
{Software Engineer Trainee} % Job title
{Blue Oscean} % Organization
{Yucatan, Mexico} % Location
{Apr. 2010 - Jul. 2010} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Developed web plug ins to add them at the main ERP solution with .NET framework and SQL querys}
\end{cvitems}
}

%------------------------------------------------


%------------------------------------------------

%\cventry
%{Freelance Software Developer} % Job title
%{} % Organization
%{S.Korea} % Location
%{Sep. 2013, Mar. 2011 - Oct. 2011} % Date(s)
%{ % Description(s) of tasks/responsibilities
%\begin{cvitems}
%\item {Conducted penetration testing on SAMSUNG KNOX, which is solution for enterprise mobile security.}
%\item {Conducted penetration testing on SAMSUNG Smart TV.}
%\end{cvitems}
%}

%------------------------------------------------

\end{cventries}